\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Userless Classificaton for the Yelp Dataset Challenge}

### 2015-12-12 paper/article_2.tex
final paper

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

@@

Our objective is to improve the categorization system of the Yelp businesses using machine learning techniques. To achieve our goal, we extract significant information out of the text reviews posted on Yelp using our own coded-up Latent Dirichlet Allocation (LDA) using Online Variational Inference, and benchmark it with an LDA using Gibbs Sampling and Non Negative Matrix Factorisation. We then present two methods for classifying restaurants. We first resorted to a supervised approach with a multinomial logistic regression on  the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in data. The second approach is unsupervised, using the Walktrap Algorithm, a community detection algorithm on network of restaurant. If the different feature extraction methods (LDA, NMF) performed differently for the supervised and unsupervised approach, we observed some very promising results. The results could be used as the first step to an automated categorization system on the Yelp website.

@@

\lettrine[nindent=0em,lines=1]{T}he classification system in Yelp is manual. When the owner of a business creates a page for his restaurant or bar, he is asked to enter a certain number of attributes or "tags". Yelp users can then alter or even add some new tags based on their experiences. As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of classification with ultimate objective to be able to create an automatised method to classify venues, based on the information contained on the business' web page and most importantly the written reviews from Yelpers.

\noindent This project can be divided in two parts, the first on feature extraction and the second on classification and clustering. In more details, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorisation (NMF) to embed the reviews into a geometrical space. We then decided to compare both supervised approaches such as Multinomial Regression and unsupervised approaches, using the Walktrap algorithm, to the problem of classification on the Yelp dataset.
%------------------------------------------------
\columnbreak
\section{Data}

@@

\begin{compactitem}
	\item 1.6 million reviews
	\item 61 000 businesses		
	\item 481 000 attributes 
	\item aggregated check-in measurements over time
\end{compactitem}

\noindent For simplicity, we chose to focus on restaurants and bars in the city of Las Vegas, Nevada. We reduced the data to a dataset of 3822 businesses, about 20 thousands reviews and 250 other features such as hours, parking availabity, take-out, ambience. If the numerical data we received from Yelp was mostly cleaned, it was not the case of the text data. Cleaning the reviews represented a significant part of this final project. We present some of the steps we followed in the process:\\

\begin{compactitem}
	\item We aggregated all the reviews about a particular business into a "super" review, in order to get a general sense of what the restaurant was about,
	\item We applied spelling corrections, removed common stopwords and generic words such as "table" or "restaurants",
	\item We attempted at only selecting common words and not adjectives in order to focus on what the venues were about and not the users' opinions,
	\item We transformed the corpus of "super reviews" into a document-term matrix that we could exploit.
\end{compactitem}

@@

To extract content from the reviews, we applied 2  methods from Topic Modeling to reduce the document term matrix into meaningful information. We first looked at LDA, using both a Gibbs sampler and Online Variational Inference (OVI) algorithm. Note that we used the Gibbs sampler as a way to benchmark our coded OVI. The motivation behind OVI is twofold. First, it appeared more appropriate to the data we were working with, indeed new reviews can always be added to the corpus in continuous flow. Second, it showed some extremely significant time improvement over the Gibbs sampler version in Python (cf figure 1). We also wanted to compare the performance of LDA with a non-probabilistic approach which is NMF.

@@

The LDA is a three-level hierarchical Bayesian model. The basic idea that documents are represented as random mixtures over latent topics and each topic is characterized by a distribution over words.\cite{LDA}\\

@@

\subsection{Parameter Estimation and algorithm:}

@@

\noindent This distribution is intractable. As mentioned above, we used two  methods to infer it: through a Gibbs sampler or variational inference. In the first case, we are estimating the hyper parameters $\theta$ and $\phi$ with samples on the different variables. Alternatively, we chose the online variational inference method which finds the variational parameters that optimize a lower bound on the loglikelihood. The setup \cite{OLLD} of the Variational Inference is as follows. We first approximate the true posterior by a simpler and factorised distribution:
$$q(\boldsymbol{z},\boldsymbol{\theta},\boldsymbol{\beta}) = q(\boldsymbol{z})q(\boldsymbol{\theta})q(\boldsymbol{\beta}) $$

@@

\noindent The $\boldsymbol{\gamma}$ parameter rule the topic assignments for each document and the $\boldsymbol{\lambda}$, the topics themselves. We then minimise the KL divergence between the distribution $q$ and the true posterior $p$ like for the usual variational inference. What differs in online variational inference is that we sample a batch of document at each step and perform the E-step as if this batch constituted the entire corpus. We present the algorithm below:

\begin{algorithm}[H]
\caption{Batched Online Variational Inference}\label{euclid}
\begin{algorithmic}[1]
\State Define $\rho_t \equiv (\tau_0 + t)^{-\kappa}$
\State Initalise $\boldsymbol{\lambda}$ randomly
\State Sample a batch $\mathcal{S}$ of documents of size S
\For{$t$=0 to $|D|/|\mathcal{S}|$}
\For {$d$ in $\mathcal{S}$}
\While {$\gamma_(d)$ hasn't converged}
\State Set $\phi^{(d)}_{twk} \propto \exp\{\mathbb{E}_q\log\theta_{tk} + \mathbb{E}_q\log\beta_{kw}\}$
\State Set $\gamma^{(d)}_{tk} = \alpha + \sum_{w} \phi^{(d)}_{twk}n_{tw}$
\EndWhile
\State Compute $\tilde{\lambda}_{kw} = \eta +\frac{D}{S}n_{tw}\phi^{(d)}_{twk}$
\EndFor
\State $\boldsymbol{\lambda} = (1-\rho_t)\boldsymbol{\lambda}+\rho_t\boldsymbol{\tilde{\lambda}}$
\EndFor
\end{algorithmic}
\end{algorithm}

\noindent where $\kappa \in (0.5,1]$ rules how fast we forget old values of $\tilde{\lambda}$ and $\tau_{0}$ how much weight one wants to put on the first iterations.

@@

We need a measure to evaluate the performance of our model and to tune the hyperparameters. We use perplexity on held-out data as a measure of our model fit. Perplexity is defined as the geometric mean of the log likelihood of the words in the held-out set of docuements given the trained model. In our case, for each document we held out 20\% of the words which constitue the test set.

@@

\noindent We used this measure to optimize the number of topics K and the hyper parameters of the optimization. We also used the perplexity on the training set to benchmark our algorithm with the Gibbs sampler in the LDA 1.0.3 package in Python:

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{img/V.png}
\caption{Cross Validation over the number of Topics}
\end{figure}

@@

\noindent We would like to also make a general comment about the Online Variational algorithm. We noticed that the OVI algorithm is extremely sensitive to the hyperparametrisation, i.e the batch size $S$, the forgetfullness parameter $\kappa$ and the early iterations weith parameter $\tau$. This was also noted by Tamara Broderick, Nicholas Boyd, Andre Wibisono and Ashia C. Wilson in their paper\cite{svi}. In addition to validating the number of topics, validating over these parameters was crucial to obtain valuable resutls.\\

\noindent We now present two different approaches to answer the question of classification using supervised and unsupervised machine learning.\\

%------------------------------------------------
\section{Supervised Classification}

@@

\noindent We chose a one-vs-all approach to tackle this multi-label task, and built one binary classifier for each label. We then assign to the entries the labels predicted by each model. The goal is here to explore how the different models perform and to tune them to come up with the best estimator. We developped our own L2 penalized logistic regression and used sklearn for the other models.

@@

\begin{figure}[H]
\begin{center}
    \begin{tabular}{| l | l | l | l |}
    \hline
    & OVI LDA & GS LDA & NMF \\ \hline
    Baseline: all False & 90,02 \% &  90.02 \% &  90.02 \% \\ \hline
    Kernel rbf SVM & 90,81\% &  90.38\% &  90.38\% \\ \hline
    Kernel rbf SVM + PCA & 90.83\% &  90.60\% &  90.57\% \\ \hline
    Logistic Regression & 90.84\% &  91.89\%  &  91.24\%\\ \hline
    Logistic Regression + PCA & 92.59\% &  92.53\% &  92.68\% \\ \hline
    Lasso & 90.82\% &  93.44\% &  92.01\% \\ \hline
	Lasso + PCA & 93.44\%  &  \textbf{94.46} \%  &  93.08\% \\ \hline
    Random Forest & 92.12\% &  93.58\% &  93.37\% \\ \hline
    Random Forest + PCA & 92.84\% &  94.66\% &  94.06\% \\ \hline
    \end{tabular}
\end{center}
\caption{Classification results for different features}
\end{figure}

@@

\noindent If we then compare the models to each other, we see that the support vector machine performs poorly and that the linear version was even closer to the baseline. This confirms that the data is not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate. The logistic regression performs better under the l1 penalization because of the sparsity of our features. Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection a very good estimator.\\

@@

Each restaurant is now represented as probability distribution over the latent topics. Using the Shannon distance (symmetric Kullback-Liebler Divergence), we created a distance matrix gathering information on how close 2 restaurants are based on their reviews. After many experimentations, we chose to transform this distance matrix into a weighted adjacency matrix:\\

@@

\noindent The choice of having a non-zero weight between two restaurants even though they are not "close" is motivated by the fact that many graph clustering algorithm and in particular the WalkTrap algorithm that we used and present next, will only work on a connected graph.\\

@@

We ran the algorithm from the \emph{igraph} package in R on the three graphs generated with the three approaches mentionned above (NMF, OVI LDA, GS LDA). The results where extremely similar. We outputted a dendogram (cf. Figure 3) representing the obtained clustering. We colored the tag of each business for a better readability.  It is not yet entirely clear to us how to get the optimum number of clusters. We were puzzled to see that the Walktrap algorithm indicated that a cut into three big clusters represented the optimum partition. Knowing the structure of the sampled restaurants, we decided to further investigate the dendogram. As one can see on Figure 3, cutting the tree at different heights, we can obtain five clear colored communities, corresponding to five of the six tags we pre-selected.\\

@@

\noindent With this method, we managed to detect 4 communities with great accuracy (over 80\%). Nevertheless, this classification still has some flaws and the most obvious one is the misclassification or even non-classification of the Sports bars (yellow). We focused a bit more on these venues and explored manually the tags associated with them. We noticed that these Sports bar were most of the time having other tags such as "Restaurants","Bar", "American" and some even "Mexican". Reviews for these venues might have been misallocated due to the proximity of types of food, drinks or "ambiance" with Mexican restaurants. It is nonetheless interesting to note that were grouped almost all together inside the Mexican restaurants, and that if we cut the three at the sixth level then they would all be gathered in 2 cliques.\\

\noindent It seems that this method will succeed in making a difference between communities of restaurants if they are almost exlusive. It seems very unlikely to discover a restaurant that one can identify as both a Mexican and a Sushi place or even a Sushi place specialising in Breakfast (unless its speciality is the takagoyaki, a type of Japanese omelette made by "rolling together several layers of cooked egg"). It was often the case that misclassified restaurant had the tag "Buffet" which is for our purpose of classification our worst ennemy as it will phagocytose many categories at once.

@@

\section{conclusion}
By using a combination of unsupervised learning and graph theory, we managed to retrieve most of the original classification that is up to now still done by hand ! This work could result in an automation tool for Yelp to label properly its database.

@@

>>>>

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text
\usepackage[toc,page]{appendix}

@@

Our objective is to improve the categorization system of the Yelp businesses using machine learning techniques. To achieve our goal, we extract significant information out of the text reviews posted on Yelp using our own coded-up Latent Dirichlet Allocation (LDA) using online variational inference (OVI), and benchmark it with the LDA using a Gibbs samplingmethod (GS) and the Non Negative Matrix Factorisation (NMF). We then present two methods for classifying restaurants. We first resorted to a supervised approach with a one-vs-all classifiers on  the text reviews combined with characteristic features of businesses - such as localisations, prices, customer type or check-in counts. The second approach is unsupervised, using the Walktrap Algorithm, a community detection algorithm on network of restaurant. If the different feature extraction methods performs differently for the supervised and unsupervised approach, we observe some very promising results. The results could be used as the first step to an automated categorization system on the Yelp website.

@@

\lettrine[nindent=0em,lines=1]{T}he classification system in Yelp is manual. When the owner of a business creates a page for his restaurant or bar, he is can provide a certain number of labels. Yelp users can then alter or even add new tags based on their experiences. As part of the Yelp Data Set Challenge Round 6, we decided to tackle the issue of entries classification. Our ultimate objective is to create an automatised method to classify the businesses, based on their properties and most importantly on their reviews from Yelpers. \\

This project can be divided in three parts. First, to extract feature, we applied various dimensionality reduction methods such as Latent Dirichlet Allocation (LDA) or Non-negative Matrix Factorisation (NMF) to embed the reviews into a geometrical space. Then, we applied supervised learning methods to evaluate how relevant are the feature to predict the labels. Last, we built an unsupervised clustering method using the Walktrap algorithm.

%------------------------------------------------
\columnbreak
\section{Data}

@@

\begin{compactitem}
    \item 1.6 million reviews;
    \item 61 000 businesses;    
    \item 481 000 attributes; 
    \item 168 customer check-in counts, corresponding to the average number of checkins per hour per day of the week.
\end{compactitem}

\noindent For simplicity, we chose to focus on restaurants and bars in the city of Las Vegas, Nevada. This reduced the data to a dataset of 3822 businesses, with about 20 thousands reviews and 250 other features per entry such as hours, parking availabity, take-out, ambience. If the numerical data provided by Yelp is mostly cleaned, it was not the case of the text data. Cleaning the reviews represented a significant part of this final project. We present some of the steps we followed in the process:\\

\begin{compactitem}
    \item We aggregated all the reviews about a particular business into a "super" review, in order to get a general sense of what the restaurant was about;
    \item We applied spelling corrections, removed common stopwords and generic words such as "table" or "restaurants";
    \item We attempted at only selecting common words and not adjectives in order to focus on what the venues were about and not the users' opinions (this process was done taking advantage of Spark to reduce the computing time);
    \item We transformed the corpus of "super reviews" into a document-term matrix that we could exploit;
    \item As we aggregated the reviews, some words may be more prevalent than others, so we scaled the words counts into the range [0, 100] for each review.
\end{compactitem}

@@

To extract content from the reviews, we applied two methods from topic modeling to reduce the document term matrix into meaningful information. We first looked at LDA, using both a Gibbs sampler (GS) and an Online Variational Inference (OVI) algorithm. Note that we used the Gibbs sampler as a way to benchmark our own version of OVI. The motivation behind OVI is twofold. First, it appeared more appropriate to the data we were working with, indeed new reviews can always be added to the corpus in continuous flow. Second, it showed some extremely significant time improvement over the Gibbs sampler version in Python. We also wanted to compare the performance of LDA with a non-probabilistic approach which is the NMF.

@@

The LDA is a three-level hierarchical Bayesian model. The basic idea is that documents are represented as random mixtures over latent topics and each topic is characterized by a distribution over words.\cite{LDA}\\

@@

\subsection{Inference}

@@

\noindent This distribution is intractable. As mentioned above, we used two  methods to infer it: through a Gibbs sampler or variational inference. In the first case, we are estimating the hyper parameters $\theta$ and $\phi$ with samples on the different variables. Alternatively, we chose the online variational inference method which finds the variational parameters that optimize a lower bound on the loglikelihood. The setup \cite{OLLD} of the variational inference is as follows. We first approximate the true posterior by a simpler and factorised distribution:

$$q(\boldsymbol{z},\boldsymbol{\theta},\boldsymbol{\beta}) = q(\boldsymbol{z})q(\boldsymbol{\theta})q(\boldsymbol{\beta}) $$

@@

\noindent The $\boldsymbol{\gamma}$ parameter rule the topic assignments for each document and the $\boldsymbol{\lambda}$, the topics themselves. We then minimise the KL divergence between the distribution $q$ and the true posterior $p$. What differs in the online variational inference is that we sample a mini-batch of document at each step and perform the E-step as if this mini-batch constituted the entire corpus. We present the algorithm below:

\begin{algorithm}[H]
\caption{Minibatch Online Variational Inference}\label{euclid}
\begin{algorithmic}[1]
\State Define $\rho_t \equiv (\tau_0 + t)^{-\kappa}$
\State Initalise $\boldsymbol{\lambda}$ randomly
\State Sample a batch $\mathcal{S}$ of documents of size S
\For{$t$=0 to $|D|/|\mathcal{S}|$}
\For {$d$ in $\mathcal{S}$}
\While {$\gamma_(d)$ hasn't converged}
\State Set $\phi^{(d)}_{twk} \propto \exp\{\mathbb{E}_q\log\theta_{tk} + \mathbb{E}_q\log\beta_{kw}\}$
\State Set $\gamma^{(d)}_{tk} = \alpha + \sum_{w} \phi^{(d)}_{twk}n_{tw}$
\EndWhile
\State Compute $\tilde{\lambda}_{kw} = \eta +\frac{D}{S}n_{tw}\phi^{(d)}_{twk}$
\EndFor
\State $\boldsymbol{\lambda} = (1-\rho_t)\boldsymbol{\lambda}+\rho_t\boldsymbol{\tilde{\lambda}}$
\EndFor
\end{algorithmic}
\end{algorithm}

\noindent where $\kappa \in (0.5,1]$ rules how fast we forget old values of $\tilde{\lambda}$ and $\tau_{0}$ how much weight one wants to put on the first iterations. $\alpha$ and $\eta$ where fixed at the same value $\frac{1}{|D|}$.

@@

We need a measure to evaluate the performance of our model and to tune the hyperparameters. We use the perplexity on held-out data as a measure of our model fit. The perplexity is defined as the geometric mean of the log likelihood of the words in the held-out set of documents given the trained model. In our case, for each document we held out 20\% of the words which constitue the validation set to apply a 5-fold cross-validation.

@@

\noindent We used this measure to optimize the number of topics K and the hyper parameters $\kappa$, $\tau$ of the optimization. We also used the perplexity on the training set to benchmark our algorithm with the Gibbs sampler in the LDA 1.0.3 package in Python:

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\linewidth]{img/V.png}
\caption{5-fold Cross Validation over the number of Topics}
\end{figure}

@@

We would like to make a general comment about the online variational algorithm. We noticed that its algorithm is extremely sensitive to the hyperparametrisation, i.e the batch size $S$, the forgetfullness parameter $\kappa$ and the early iterations weith parameter $\tau$. This was also noted by Tamara Broderick, Nicholas Boyd, Andre Wibisono and Ashia C. Wilson in their paper\cite{svi}. In addition to validating the number of topics, validating over these parameters was crucial to obtain valuable results.\\

We now present two different approaches to answer the question of classification using supervised and unsupervised machine learning methods.\\

%------------------------------------------------
\section{Classification}

@@

\noindent We chose a one-vs-all approach to tackle this multi-label task, and built one binary classifier for each label. We then assign to the entries the labels predicted by each model. The goal is here to explore how the different models perform and to tune them to come up with the best estimator. We developped our own L2 penalized logistic regression and used \emph{scikit-learn} \cite{sklearn} for the other models.

@@

\begin{figure}[H]
\begin{center}
    \begin{tabular}{| l | l | l | l |}
    \hline
    & OVI LDA & GS LDA & NMF \\ \hline
    Baseline: all False & 90,02 \% &  90.02 \% &  90.02 \% \\ \hline
    Kernel rbf SVM & 91.00\%  &  90.73\%  &  90.67\% \\ \hline
    Kernel rbf SVM + PCA & 90.62\%  &  90.85\%  &  90.85\% \\ \hline
    Logistic Regression & 91.39\%  &  91.86\%  &  91.86\%\\ \hline
    Logistic Regression + PCA & 92.37\%  &  92.89\%  &  93.16\% \\ \hline
    Lasso & 91.18\%  &  93.75\%  &  92.40\% \\ \hline
	Lasso + PCA & 92.53\%  &  94.83\%  &  93.35\% \\ \hline
    Random Forest & 92.12\% &  93.58\% &  93.37\% \\ \hline
    Random Forest + PCA & 92.84\% &  \textbf{94.66} \% &  94.06\% \\ \hline
    \end{tabular}
\end{center}
\caption{Classification results for different features}
\end{figure}

@@

\noindent If we then compare the models to each other, we see that the support vector machine performs poorly and that the linear version was even closer to the baseline. This confirms that the data is not linearly separable and even their projection by the rbf function used in sklearn library (gamma function) is quite impossible to separate. The logistic regression performs better under the l1 penalization because of the sparsity of our features. Lastly, the random forest managed to reduce the common overfitting of the decision trees while aggregating them and provides on the PCA projection the best estimator.\\

@@

Each restaurant is now represented as a probability distribution over the latent topics. Using the Shannon distance (symmetric Kullback-Liebler Divergence), we created a distance matrix gathering information on how close two restaurants are based on their reviews. After many experimentations, we chose to transform this distance matrix into a weighted adjacency matrix:\\

@@

\noindent The choice of having a non-zero weight between two restaurants even though they are not "close" is motivated by the fact that many graph clustering algorithm, in particular the WalkTrap algorithms that we used, only work on a connected graph.\\

@@

We ran the algorithm from the \emph{igraph} \cite{igr} package in R on the three graphs generated with the three approaches mentionned above (NMF, OVI LDA, GS LDA). The results where extremely similar. We outputted a dendogram (cf. Annex) representing the obtained clustering. We colored the tag of each business for a better readability.  It is not yet entirely clear to us how to get the optimum number of clusters. We were puzzled to see that the Walktrap algorithm indicated that a cut into three big clusters represented the optimum partition. Knowing the structure of the sampled restaurants, we decided to further investigate the dendogram. As one can see on Figure 3, cutting the tree at different heights, we can obtain five clear colored communities, corresponding to five of the six tags we pre-selected.\\

@@

\noindent With this method, we managed to detect 4 communities with great accuracy (over 80\%). Nevertheless, this classification still has some flaws and the most obvious one is the misclassification or even non-classification of the Sports bars (yellow). We focused a bit more on these venues and explored manually the tags associated with them. We noticed that these Sports bar have most of the time other tags such as "Restaurants","Bar", "American" and some even "Mexican". Reviews for these venues might have been misallocated due to the proximity of types of food, drinks or "ambiance" with Mexican restaurants. It is nonetheless interesting to note that they were grouped almost all together inside the Mexican restaurants, and that if we cut the tree at the sixth level then they would all be gathered in 2 cliques.\\

\noindent It seems that this method will succeed in making a difference between communities of restaurants if they are almost exlusive. It seems very unlikely to discover a restaurant that one can identify as both a Mexican and a Sushi place or even a Sushi place specialising in Breakfast (unless its speciality is the takagoyaki, a type of Japanese omelette made by "rolling together several layers of cooked egg"). It was often the case that misclassified restaurants had the tag "Buffet" which is for our purpose of classification our worst ennemy as it will phagocytose many categories at once.

@@

\section{conclusion}

This study illustrates different methods to extract feature from a set of documents. The results confirmed that the latent Dirichlet allocation manages to grasp the underlying features. The comparison with the supervised learning methods confirmed the importance of the feature extraction part in a machine learning problem. It also corroborates the assumption that the features of the businesses could be used to infer their category labels. Finally, the unsupervised clustering process we developped provides encouraging results and could result in an automation tool for Yelp to label properly its database.

@@

\newpage
